Supplementary Materials

### 2022-12-08 manuscript/supplementary.tex
ms

@@

>>>>

\begin{figure}[!htb]
  \centering
  \includegraphics{figures/supplementary/chr1_diversity_filtering.pdf}

  \caption{Estimates of chromosome 1 YRI diversity in non-overlapping megabase
    windows, under different filtering criteria. The filtering criteria are,
    (1) ``neutral, accessible" which includes only putatively neutral sites, and
    ignores regions masked as inaccessible, (2) ``accessible" which is only ignores
  sites masked as inaccessible, and (3) ``no filtering" which uses all available
data. Note that filtering changes the absolute level of diversity, but has more
minor effects on regional patterns of diversity at the megabase scale.}

  \label{suppfig:chr1-diversity}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics{figures/supplementary/diversity_trimming_dist.pdf}
  \caption{}
  \label{suppfig:trimming}
\end{figure}
